\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-04-25 paper/main.tex
Updated run-tool example to include an API supported by FreeFuzz

The following script runs FreeFuzz on all bugs associated with version
2.2.0 of \torch.  The command \CodeIn{run-tool} takes the library
version as an input, along with the name of the docker container
(already created), the name of the library, and the user-provided
script containing the commands to run the tool
(\CodeIn{run\_freefuzz\_docker.sh}. The script reports how
many bugs that are reproducible with this version of the library were successfully
reproduced by the given tool.  Tool execution proceeds as
follows. First, a Docker container associated with the tool is created using
\CodeIn{install\_freefuzz\_docker.sh}. Next, a reproducible bug is tested using
the specified library version as input to verify the setup.
Following this, the preprocessing script (\CodeIn{preprocess.py}) is executed 
to extract error types and identify buggy APIs for the given library version.
The environment inside the Docker container is then updated to match the specified version, 
ensuring compatibility before running the fuzzing tool. Once execution is complete, a postprocessing 
script (\CodeIn{postprocess.py}) is run to analyze the execution log against the ground truth, 
determining whether the bugs were successfully reproduced.

\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
$> run-tool -c freefuzz -l pytorch -v 2.2.0 \
   --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
\end{lstlisting}

% The script \CodeIn{run\_freefuzz\_docker.sh} contains instructions to run the preprocessing script, the tool, and the postprocessing script.
The output looks like the following:
\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
Using bug-id 120903 for library pytorch version 2.2.0...
RuntimeError: !needs_dynamic_casting<func_t>::check(iter) INTERNAL 
ASSERT FAILED at "../aten/src/ATen/native/cpu/Loops.h":310, please
report a bug to PyTorch.
====== 1 passed in 1.09s ======
Updating environment in the container of the testing tool...
Running the testing tool on the environment of the bug
APIs under test:
torch.fake_quantize_per_channel_affine
torch.all
torch.compile
Testing on  ['torch']
torch.atanh...
No violation of precision-oracle in the compare-bug category
No violation of precision-oracle in the potential-bug category
No violation of cuda-oracle in the compare-bug category
No violation of cuda-oracle in the potential-bug category
No violation of crash-oracle in the compare-bug category
No violation of crash-oracle in the potential-bug category
-> torch.fake_quantize_per_channel_affine did not face any failures
-> torch.all did not face any failures
-> torch.compile did not face any failures
Reproduced 0 out of 3 bugs
\end{lstlisting}

@@

The execution log shows that the tool did not reproduce any of the
three bugs that were expected to be reproduced since the three buggy APIs \CodeIn{torch.fake\_quantize\_per\_channel\_affine}, \CodeIn{torch.all}, and \CodeIn{torch.compile} are not supported by FreeFuzz. The outputs of the tool are saved in the container and can be inspected manually to further inspect the execution log. From this result, the developer can decide to add support for these three APIs in FreeFuzz and run the tool again to check if the bugs can be reproduced now. This will allow developers to decide on which APIs to add support for.

>>>>

The following script runs FreeFuzz on all bugs associated with version
2.2.1+cu121 of \torch.  The command \CodeIn{run-tool} takes the library
version as an input, along with the name of the docker container
(already created), the name of the library, and the user-provided
script containing the commands to run the tool
(\CodeIn{run\_freefuzz\_docker.sh}. The script reports how
many bugs that are reproducible with this version of the library were successfully
reproduced by the given tool.  Tool execution proceeds as
follows. First, a Docker container associated with the tool is created using
\CodeIn{install\_freefuzz\_docker.sh}. Next, a reproducible bug is tested using
the specified library version as input to verify the setup.
Following this, the preprocessing script (\CodeIn{preprocess.py}) is executed 
to extract error types and identify buggy APIs for the given library version.
The environment inside the Docker container is then updated to match the specified version, 
ensuring compatibility before running the fuzzing tool. Once execution is complete, a postprocessing 
script (\CodeIn{postprocess.py}) is run to analyze the execution log against the ground truth, 
determining whether the bugs were successfully reproduced.

\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
$> run-tool -c freefuzz -l pytorch -v 2.2.1+cu121 \
   --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
\end{lstlisting}

% The script \CodeIn{run\_freefuzz\_docker.sh} contains instructions to run the preprocessing script, the tool, and the postprocessing script.
The output looks like the following:
\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
Using bug-id 121725 for library pytorch version 2.2.1+cu121
...
RuntimeError: Please look up dimensions by name, got: name = None.
====== 1 passed in 0.63s ======
Updating environment in the container of the testing tool
...
Running the testing tool on the environment of the bug
APIs under test:
torch.logsumexp
torch.autograd.grad
Testing on  ['torch']
torch.multinomial
...
No violation of precision-oracle in the compare-bug category
No violation of precision-oracle in the potential-bug category
No violation of cuda-oracle in the compare-bug category
No violation of cuda-oracle in the potential-bug category
No violation of crash-oracle in the compare-bug category
No violation of crash-oracle in the potential-bug category
-> torch.logsumexp did not face any failures
-> torch.autograd.grad did not face any failures
Reproduced 0 out of 2 bugs
\end{lstlisting}

@@

The execution log shows that the tool did not reproduce any of the
two bugs that were expected to be reproduced. 
% since the three buggy APIs \CodeIn{torch.fake\_quantize\_per\_channel\_affine}, \CodeIn{torch.all}, and \CodeIn{torch.compile} are not supported by FreeFuzz. 
Among the two buggy APIs, FreeFuzz supports \CodeIn{torch.logsumexp} but the bug could not be reproduced, whereas FreeFuzz does not support \CodeIn{torch.autograd.grad}.
The outputs from the tool are saved in the container so that the execution log can be inspected further manually.
% can be inspected manually to further inspect the execution log. 
From this result, the developer can debug and refine their technique to catch bugs that it missed, as well as add support for APIs that are currently unsupported.
